### 2013-01-09 edupar-13/intro.tex
intro.tex: typo reported by Ben

In this paper we describe our experience teaching concurrent programming at the operating systems level to advanced undergraduate students at Carnegie Mellon University (CMU).
In 15-410, the Operating Systems Design and Implementation class at CMU, students complete an aggressively low-level kernel project, which runs on real hardware, in which they implement threads and processes.
Presented with a kernel specification, called Pebbles~\cite{kspec}, students build a threading and synchronization library that runs in user space on top of a Pebbles-compliant kernel in a two-week project, and subsequently, in a six-week project, write their own multi-threaded kernel implementation.
During these projects students face demanding synchronization problems, including how to implement locking primitives and how to coordinate the possibly-simultaneous exiting of parent and child processes.
Finally, in another two-week project, students implement a small extension to their Pebbles kernel. This project changes every semester, and in the past has included extending their kernel serve as a hypervisor, or to support symmetric multiprocessing.

>>>>

In this paper we describe our experience teaching concurrent programming at the operating systems level to advanced undergraduate students at Carnegie Mellon University (CMU).
In 15-410, the Operating Systems Design and Implementation class at CMU, students complete an aggressively low-level kernel project, which runs on real hardware, in which they implement threads and processes.
Presented with a kernel specification, called Pebbles~\cite{kspec}, students build a threading and synchronization library that runs in user space on top of a Pebbles-compliant kernel in a two-week project, and subsequently, in a six-week project, write their own multi-threaded kernel implementation.
During these projects students face demanding synchronization problems, including how to implement locking primitives and how to coordinate the possibly-simultaneous exiting of parent and child processes.
Finally, in another two-week project, students implement a small extension to their Pebbles kernel. This project changes every semester, and in the past has included extending their kernel to serve as a hypervisor, or to support symmetric multiprocessing.
